---
title: "Untitled"
author: "Kolor Nguyen"
date: "3/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(shiny)
library(shinythemes)

```

```{r}
time1 <- time %>% separate(date, into = c("Year","Month","Day"),sep = "-",convert = TRUE) %>% 
              mutate(Days_since_1st_case=Day + (Month-1)*31 - 19) %>% 
              pivot_longer(col = c(Seoul,Daegu,Busan,Incheon,Gwangju,Daejeon,Ulsan,Sejong,Gyeonggi.do,Gangwon.do,Chungcheongbuk.do,Chungcheongnam.do,Jeollabuk.do,Jeollanam.do,Gyeongsangbuk.do,Gyeongsangnam.do,Jeju.do),names_to = "Region", values_to = "Confirmed_cases")
time1
Regions <- c("Seoul","Daegu","Busan","Incheon","Gwangju","Daejeon","Ulsan","Sejong","Gyeonggi.do","Gangwon.do","Chungcheongbuk.do","Chungcheongnam.do","Jeollabuk.do","Jeollanam.do","Gyeongsangbuk.do","Gyeongsangnam.do","Jeju.do")
time2 <- time1 %>% filter(Region %in% Regions)
```

```{r}
ui <- fluidPage(theme = shinytheme("slate"),
  
  headerPanel("Number of confirmed Coronavirus Disease 2019 (COVID-19) cases in South Korea"),
  
  sidebarLayout(

    sidebarPanel(

           
           numericInput("starttime", 
                        h4("Enter starting number of days since the 1st case:"), 
                        value=35, 
                        min=1, 
                        max=55, 
                        step=1),
  
           numericInput("endtime", 
                        h4("Enter ending number of days since the 1st case:"), 
                        value=55, 
                        min=1, 
                        max=55, 
                        step=1),
           checkboxGroupInput('region', h4('Regions to display:'), sort(Regions),
                              selected=c("Seoul","Busan","Incheon","Gwangju","Daejeon","Ulsan","Sejong","Gangwon.do","Chungcheongbuk.do","Chungcheongnam.do","Jeollabuk.do","Jeollanam.do","Gyeongsangnam.do","Jeju.do"))
    ),
    
    mainPanel(
      plotOutput("plot")
    )
  ))

server <- function(input, output) {
  
  output$plot <- renderPlot({
    Start_time <- input$starttime
    End_time <- input$endtime
    Regions <- input$region
    
    region_df <-  time2 %>%
      filter(Days_since_1st_case >= Start_time, Days_since_1st_case <= End_time, Region %in% Regions)
    ggplot(data=region_df, aes(x=Days_since_1st_case, y=Confirmed_cases, color=Region)) + 
    geom_line(size=1) + theme_bw() + 
    xlab("Days since the 1st case in South Korea (January 20, 2020)") + 
    ylab("Number of confirmed cases") + 
    theme(axis.text=element_text(size=10,face="bold"),
        axis.title=element_text(size=14,face="bold"),legend.title = element_text(size=12,face="bold"),legend.text = element_text(size=11)) + theme(aspect.ratio = 1) +  
        theme(plot.background=element_rect(fill="azure3"))
  })
}

shinyApp(ui = ui, server = server)
